### 2021-08-27 ms/ms.Rmd
added model summary table

processed_data_files = tibble(file_name = list.files("processed-data"))
objects_files = tibble(file_name = list.files("objects"))

@@

@@

```{r, modeloutput}

# stomata_anatomy_metadata |>
#   dplyr::mutate(Source = stringr::str_c("@", source), Taxa = taxa) |>
#   dplyr::select(Source, Taxa) |>
#   knitr::kable(format = "markdown", caption = "Primary sources of stomatal anatomical data and the taxa covered by each source.")
tibble(x = 1:2, y = 3:4) |>
  knitr::kable(format = "markdown", caption = "Model output")
```

>>>>

@@

# 17_summarize-fit ----
mo = read_rds("objects/modeloutput.rds")

@@

\begin{table}[ht]
\caption{\label{tab:modeloutput} Parameter estimates and 95\% highest posterior density (HPD) intervals. For each trait ($D_\mathrm{ab}$, $D_\mathrm{ad}$, $L_\mathrm{ab}$, $L_\mathrm{ad}$) we estimated the average (median) divergence between taxon pairs, denoted $\Delta \text{log(trait)}$. See Table \ref{tab:traits} for symbol definitions. The second section is the standard deviation of $\Delta \text{log(trait)}$. The third section is the estimated coefficient of pair age (millions of years) on the standard devition on a log-link scale. The fourth section is the estimated correlation coefficient between $\Delta \text{log(trait)}$ of all pairwise trait combinations. The final section is the estimated $\nu$ family of the Student $t$ distribution.}
\begin{center}
\begin{tabular}{lll}

  \toprule
  Trait(s) & Estimate & 95\% HPD interval \\
  \midrule

  \multicolumn{3}{l}{Average $\Delta \text{log(trait)}$} \\
  \\
  $D_\mathrm{ab}$ & `r mo$mu["D_ab", "value"]`  & `r mo$mu["D_ab", "hdi"]`  \\
  $D_\mathrm{ad}$ & `r mo$mu["D_ad", "value"]`  & `r mo$mu["D_ad", "hdi"]`  \\
  $L_\mathrm{ab}$ & `r mo$mu["L_ab", "value"]`  & `r mo$mu["L_ab", "hdi"]`  \\
  $L_\mathrm{ad}$ & `r mo$mu["L_ad", "value"]`  & `r mo$mu["L_ad", "hdi"]`  \\
  \\
  \multicolumn{3}{l}{Standard deviation of $\Delta \text{log(trait)}$} \\
  \\
  $D_\mathrm{ab}$ & `r mo$sigma["D_ab", "value"]`  & `r mo$sigma["D_ab", "hdi"]`  \\
  $D_\mathrm{ad}$ & `r mo$sigma["D_ad", "value"]`  & `r mo$sigma["D_ad", "hdi"]`  \\
  $L_\mathrm{ab}$ & `r mo$sigma["L_ab", "value"]`  & `r mo$sigma["L_ab", "hdi"]`  \\
  $L_\mathrm{ad}$ & `r mo$sigma["L_ad", "value"]`  & `r mo$sigma["L_ad", "hdi"]`  \\
  \\
  \multicolumn{3}{l}{Effect of pair age on standard deviation of $\Delta \text{log(trait)}$} \\
  \multicolumn{3}{l}{log-link scale} \\
  \\
  $D_\mathrm{ab}$ & `r mo$age["D_ab", "value"]`  & `r mo$age["D_ab", "hdi"]`  \\
  $D_\mathrm{ad}$ & `r mo$age["D_ad", "value"]`  & `r mo$age["D_ad", "hdi"]`  \\
  $L_\mathrm{ab}$ & `r mo$age["L_ab", "value"]`  & `r mo$age["L_ab", "hdi"]`  \\
  $L_\mathrm{ad}$ & `r mo$age["L_ad", "value"]`  & `r mo$age["L_ad", "hdi"]`  \\
  \\
  \multicolumn{3}{l}{Correlation between $\Delta \text{log(trait)}$} \\
  \\
  $D_\mathrm{ab}-D_\mathrm{ad}$ & 
  `r mo$cor["D_ab-D_ad", "value"]`  & `r mo$cor["D_ab-D_ad", "hdi"]`  \\
  $D_\mathrm{ab}-L_\mathrm{ab}$ & 
  `r mo$cor["D_ab-L_ab", "value"]`  & `r mo$cor["D_ab-L_ab", "hdi"]`  \\
  $D_\mathrm{ab}-L_\mathrm{ad}$ & 
  `r mo$cor["D_ab-L_ad", "value"]`  & `r mo$cor["D_ab-L_ad", "hdi"]`  \\
  $D_\mathrm{ad}-L_\mathrm{ab}$ & 
  `r mo$cor["D_ad-L_ab", "value"]`  & `r mo$cor["D_ad-L_ab", "hdi"]`  \\
  $D_\mathrm{ad}-L_\mathrm{ad}$ & 
  `r mo$cor["D_ad-L_ad", "value"]`  & `r mo$cor["D_ad-L_ad", "hdi"]`  \\
  $L_\mathrm{ab}-L_\mathrm{ad}$ & 
  `r mo$cor["L_ab-L_ad", "value"]`  & `r mo$cor["L_ab-L_ad", "hdi"]`  \\
  \\
  \multicolumn{3}{l}{Student $t$ famil parameter $\nu$} \\
  \\
  $-$ & `r mo$nu["nu", "value"]`  & `r mo$nu["nu", "hdi"]`  \\

\bottomrule

\end{tabular}
\end{center}
\end{table}

### 2021-08-27 ms/ms.tex
added model summary table

\begin{longtable}[]{@{}rr@{}}
\caption{\label{tab:modeloutput}Model output}\tabularnewline
\toprule
x & y \\
\midrule
\endfirsthead
\toprule
x & y \\
\midrule
\endhead
1 & 3 \\
2 & 4 \\
\bottomrule
\end{longtable}

>>>>

\begin{table}[ht]
\caption{\label{tab:modeloutput} Parameter estimates and 95\% highest posterior density (HPD) intervals. For each trait ($D_\mathrm{ab}$, $D_\mathrm{ad}$, $L_\mathrm{ab}$, $L_\mathrm{ad}$) we estimated the average (median) divergence between taxon pairs, denoted $\Delta \text{log(trait)}$. See Table \ref{tab:traits} for symbol definitions. The second section is the standard deviation of $\Delta \text{log(trait)}$. The third section is the estimated coefficient of pair age (millions of years) on the standard devition on a log-link scale. The fourth section is the estimated correlation coefficient between $\Delta \text{log(trait)}$ of all pairwise trait combinations. The final section is the estimated $\nu$ family of the Student $t$ distribution.}
\begin{center}
\begin{tabular}{lll}

  \toprule
  Trait(s) & Estimate & 95\% HPD interval \\
  \midrule

  \multicolumn{3}{l}{Average $\Delta \text{log(trait)}$} \\
  \\
  $D_\mathrm{ab}$ & -0.0015  & $-0.03-0.031$  \\
  $D_\mathrm{ad}$ & -0.0019  & $-0.04-0.038$  \\
  $L_\mathrm{ab}$ & -0.0038  & $-0.016-0.0096$  \\
  $L_\mathrm{ad}$ & -0.0017  & $-0.015-0.011$  \\
  \\
  \multicolumn{3}{l}{Standard deviation of $\Delta \text{log(trait)}$} \\
  \\
  $D_\mathrm{ab}$ & 0.230  & $0.2-0.26$  \\
  $D_\mathrm{ad}$ & 0.280  & $0.24-0.32$  \\
  $L_\mathrm{ab}$ & 0.094  & $0.083-0.1$  \\
  $L_\mathrm{ad}$ & 0.094  & $0.084-0.11$  \\
  \\
  \multicolumn{3}{l}{Effect of pair age on standard deviation of $\Delta \text{log(trait)}$} \\
  \multicolumn{3}{l}{log-link scale} \\
  \\
  $D_\mathrm{ab}$ & 0.0098  & $0.0039-0.017$  \\
  $D_\mathrm{ad}$ & 0.0170  & $0.01-0.024$  \\
  $L_\mathrm{ab}$ & 0.0140  & $0.0091-0.02$  \\
  $L_\mathrm{ad}$ & 0.0150  & $0.0096-0.021$  \\
  \\
  \multicolumn{3}{l}{Correlation between $\Delta \text{log(trait)}$} \\
  \\
  $D_\mathrm{ab}-D_\mathrm{ad}$ & 
   0.36  & $0.26-0.46$  \\
  $D_\mathrm{ab}-L_\mathrm{ab}$ & 
  -0.55  & $-0.63--0.47$  \\
  $D_\mathrm{ab}-L_\mathrm{ad}$ & 
  -0.43  & $-0.53--0.34$  \\
  $D_\mathrm{ad}-L_\mathrm{ab}$ & 
  -0.31  & $-0.41--0.2$  \\
  $D_\mathrm{ad}-L_\mathrm{ad}$ & 
  -0.34  & $-0.45--0.24$  \\
  $L_\mathrm{ab}-L_\mathrm{ad}$ & 
   0.87  & $0.84-0.9$  \\
  \\
  \multicolumn{3}{l}{Student $t$ famil parameter $\nu$} \\
  \\
  $-$ & 3.7  & $2.8-4.7$  \\

\end{tabular}
\end{center}
\end{table}
